First Order Alternation

### 2018-09-26 quantifiers/draft.tex
ok

In a nutshell, a lazy annotation procedure systematically explores the
set of execution paths (in our case, sequences of input events) in
search of an accepting execution. Each path has a corresponding path
formula that defines all words accepted along that path. If the
current path formula is satisfiable, the automaton accepts a word and
is not empty. Otherwise, the path is said to be \emph{spurious}. When
a spurious path is encountered, the search backtracks and the path is
annotated with a set of learned facts, that marks this path as
spurious in all future searches. The semi-algorithm uses moreover a
coverage relation between paths, that optimize the search (the
continuations of already covered paths are never explored) and
sometimes provide a sound termination argument, when the automaton is
empty.

We check emptiness of first-order alternating automata using a version
of the \impact~ lazy annotation semi-algorithm \cite{McMillan06}. The
detailed pseudocode has been given for a simpler model of boolean
alternating automata extended with variables \cite{IosifXu18}. To save
space, we do not present the details of this algorithm (given in
Appendix \ref{app:pseudocode}) and shall content ourselves of several
high-level definitions.

>>>>

In a nutshell, a lazy annotation procedure systematically explores the
set of execution paths (in our case, sequences of input events) in
search of an accepting execution. Each path has a corresponding path
formula that defines all words accepted along that path. If the path
formula is satisfiable, the automaton accepts a word. Otherwise, the
path is said to be \emph{spurious}. When a spurious path is
encountered, the search backtracks and the path is annotated with a
set of learned facts, that marks this path as infeasible. The
semi-algorithm uses moreover a coverage relation between paths,
ensuring that the continuations of already covered paths are never
explored. Sometimes this coverage relation provides a sound
termination argument, when the automaton is empty.

We check emptiness of first-order alternating automata using a version
of the \impact~ lazy annotation semi-algorithm \cite{McMillan06}. An
analogous procedure is given in \cite{IosifXu18}, for a simpler model
of alternating automata, that uses only predicates or arity zero
(booleans) and no transition quantifiers. For simplicity, we do not
present the details of this algorithm (see Appendix
\ref{app:pseudocode}) and shall content ourselves of several
high-level definitions.
